A Fredholm operator approach to the plate buckling problem

### 2018-08-24 doc/draft-01/08append.tex
updating appendix

\subsection{Existence results}

>>>>

\begin{lem}
Suppose that $\Omega$ is a multiply connected domain with outer boundary
$\Gamma_{0}$ and $n-$ obstacle boundaries $\Gamma_{j}$, $j=1,2,\ldots n$. 
Suppose that $k$ is a Stokes eigenvalue for the region $\Omega$ and 
let $\bu$ be the corresponding eigenfunction. 
Then, the stream function associated with the velocity $\bu$ defined by
$w = \left(\nabla^{\perp} \right)^{-1} \bu$ exists and is single valued. 
Furthermore, $k$ is also a buckling eigenvalue if and only if
\begin{equation}
\int_{\Gamma_{j}} w_{j} ds = 0 \quad \forall j=1,2,\ldots n \, .
\end{equation}
\end{lem}

\begin{proof}
Since $\bu$ is a Stokes eigenfunction, it satisfies
\begin{equation}
\int_{\Gamma_{j}} \bu \cdot \bn ds = 0 \quad j=1,2\ldots n \, .
\end{equation}
Thus, there exists a single valued stream function associated with the
velocity field $\bu$ such that 
\begin{equation}
\nabla^{\perp} w = \bu \, .
\end{equation}
Furthermore, since $\bu$ satisfies the Helmholtz-Stokes equations, 
$w$ satisfies
\begin{align}
\Delta (\Delta + k^{2} ) w &= 0 \, , \quad \bx \in \Omega \\
\nabla^{\perp} w = \bu &=0 \, ,\quad \bx \in \Gamma \, ,
\end{align}
where $\Gamma = \cup_{j=0}^{n} \Gamma_{j}$ is the boundary of $\Omega$.
In particular $w= c_{j}$ and $dw/dn = 0$ for $\bx \in \Gamma_{j}$ for
some constant $c_{j}$.
Thus $k$ is also a buckling eigenvalue if and only if 
\begin{equation}
c_{j} = \frac{1}{|\Gamma_{j}|}\int_{\Gamma_{j}} w ds =  0 \, .
\end{equation}
\end{proof}

The above result can be restated as a 
a uniqueness result for the 
solutions to the Helmholtz-Stokes equations whenever $k$ is
not a buckling value and the stream function associated with the
velocity satisfies additional integral constraints.
We state the result in the following lemma.
\begin{lem}
\label{lem:conshelmbieig}
Suppose that $k$ is not a buckling eigenvalue. 
Further suppose that $\bu$ satisfies
\begin{align}
\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \\
\nabla \cdot \bu &=0 \quad \bx \in \Omega \\
\bu &=0 \quad \bx \in \Gamma \\
\frac{1}{|\Gamma_{j}|}
\int_{\Gamma_{j}} \left(\nabla^{\perp} \right)^{-1} \bu &= c \quad
j=0,1,2,\ldots n\, ,
\end{align}
where $c$ is a constant independent of the boundary component $\Gamma_{j}$.
Then $\bu \equiv 0$ for all $\bx \in \Omega$.
\end{lem}

\begin{lem}
Suppose that $k$ is not a buckling eigenvalue. 
Let $\mathbf{K}_{\Gamma}$, $\mathbf{B}$, $\mathbf{D}$, 
and $\mathbf{F}$ denote the operators defined in~\cref{eq:eqns}.
Then the block system
\begin{equation}
\begin{bmatrix}
-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} + 
\mathbf{K}_{\Gamma} & \mathbf{B} \\
\mathbf{D} & \mathbf{F} 
\end{bmatrix} \, ,
\label{eq:IntEqBiharm1newapp}
\end{equation}
is an invertible Fredholm operator.
\end{lem}
\begin{proof}
It is simple to
show that the linear system \cref{eq:IntEqBiharm1newapp}
is Fredholm. The block which contains
$-1/2 \mathbf{I}_{\mathcal{X}\times\mathcal{X}}
+ \mathbf{K}_\Gamma$ is Fredholm due to 
\cref{lem:stokehelmsrep}. 
The off-diagonal blocks,
denoted by $\mathbf{B}$ and $\mathbf{D}$, 
are trivially compact because either the domain 
or range of the operator is finite dimensional. 
Finally, $\mathbf{F}$ is 
Fredholm because it is a finite-dimensional linear
operator. 
Therefore, the full system is Fredholm.

Due to the Fredholm alternative,
it is suffices to establish the injectivity of
the system \cref{eq:IntEqBiharm1new} to prove that 
it is invertible.

Suppose that $\bmu,\bc$ satisfy
\begin{equation}
\begin{bmatrix}
-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} + 
\mathbf{K}_{\Gamma} & \mathbf{B} \\
\mathbf{D} & \mathbf{F} 
\end{bmatrix}  
\bbmat
\bmu \\
\bc
\ebmat
=
\bbmat
0 \\ 0
\ebmat \, ,
\label{eq:IntEqBiharm1newapp2}
\end{equation}
then $w$ defined by~\cref{eq:wrep}, satsifies the Helmholtz-Biharmonic
equation~\cref{eq:helmbi,eq:helmbibc1,eq:helmbibc2} 
with boundary conditions $f=g=0$.
Since $k$ is not a buckling eigenfrequency, we conclude that $w\equiv 0$ 
for $\bx \in \Omega$.

Let $\bu = \nabla^{\perp} w$ and let 
$\bu^{\mu} = ik \mathbf{S} [\bmu] + \mathbf{D}[\bmu] = u 
-\mathbf{B} \bc - \mathbf{W}[\bmu]$.
For each $\ell = 1,\ldots,N$, 
let $\tilde{\Gamma}_{\ell} \subset \Omega$ be a curve which satisfies 
$n\left(z_{j}, \tilde{\Gamma}_{\ell}\right) = \delta_{j\ell}$, 
where $n\left(z,\gamma\right)$ represents the winding number 
of the curve $\gamma$ about z. 
Because $\mathbf{u} = \nabla^{\perp} w$ and $w\equiv 0$ in $D$,
we have 
\begin{equation}
\int_{\tilde{\Gamma}_\ell} (\Delta + k^2) \bu \cdot \boldsymbol{\tau} \, dS = 0 .
\end{equation}
We observe that $\bu^\mu$ corresponds
to a Helmholtz-Stokes velocity field in $D$. Let $p$ be 
its associated pressure. Then
\begin{equation}
\int_{\tilde{\Gamma}_k} (\Delta+k^2) \bu^\mu 
\cdot \boldsymbol{\tau}
\, dS = \int_{\tilde{\Gamma}_k} \nabla p \cdot \boldsymbol{\tau} \, dS = 0 \, .
\end{equation}
Further, a simple calculation shows that 
\begin{equation}
\int_{\tilde{\Gamma}_\ell} (\Delta + k^{2}) \nabla^{\perp} c_j 
\log (r_j) \cdot \boldsymbol{\tau} \, dS = 
2 \pi k^2 c_{j} \delta_{j\ell} \, ,
\end{equation}
for $j = 1, \ldots, N$.
Combining these equations, we conclude that
\begin{equation}
0 = \int_{\tilde{\Gamma}_j} (\Delta +k^2) \bu \cdot 
\boldsymbol{\tau} \, dS =
\int_{\tilde{\Gamma}_j} (\Delta +k^2)( \mathbf{u}^\mu + \mathbf{B}\mathbf{c} )
\cdot \boldsymbol{\tau} \, dS =  
2\pi k^2 c_j \, .
\end{equation}
Thus $c_j = 0$ for $j=1,2,\ldots N$.

The system of equations~\cref{eq:IntEqBiharm1newapp2} then reads
\begin{align}
\left(-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} 
+ \mathbf{K}_\Gamma \right) 
\boldsymbol{\mu} &= 0 \, . \label{eq:IntEq1} \\
\mathbf{B} \bmu &= -c_{0} \left(|\Gamma_{0}|, |\Gamma_{2}| \ldots |\Gamma_{n}| 
\,. 
\right)
\end{align}
This implies that $\bu^{\mu}$ defined above satisfies the
Helmholtz-Stokes equation with the integral constraints
\begin{equation}
\frac{1}{|\Gamma_{j}|} 
\int_{\Gamma_{j}} \left(\nabla^{\perp}\right)^{-1} \bu ds = -c_{0} 
\, .
\end{equation}
From~\cref{lem:conshelmbieig}, we conclude that $\bu^{\mu} \equiv 0$ 
for $\bx \in \Omega$.
Using properties of the layer potentials, $\bu^{\mu}$ satisfies that
Helmholtz-Stokes equation in $\R^{2} \setminus \Omega$
along with the radiation condition~\cref{def:radcond}.
Let $\bu^{\mu,+}, \ff^{\mu,+}$ denote the exterior limits, i.e.
\begin{align}
\bu^{\mu,+}(\bx_{0}) &=
\lim_{\substack{\bx \to \bx_{0}\\ \bx \in \R^{2} \setminus \Omega}}
\bu(\bx)\ , , \\ 
\ff^{\mu,+}(\bx_{0}) &=
\lim_{\substack{\bx \to \bx_{0}\\ \bx \in \R^{2} \setminus \Omega}}
\ff(\bx) \, , \\ 
\end{align}
where $\bx_{0} \in \Gamma$.
Using the jump conditions for the layer potentials, we conclude that
\begin{equation}
\ff^{\mu,+}(\bx) = ik \bmu (\bx) \quad \text{and} \quad 
\bu^{\mu,+}(\bx) = \bmu
(\bx) \quad \bx \in \Gamma \,. 
\label{eq:bcaux}
\end{equation}
Thus, in the exterior of the outer-boundary $\Gamma_{0}$, 
$\bu^{\mu,+}$ satisfies the Helmholtz-Stokes equation with the impendance
boundary condition
\begin{equation}
\ff^{\mu,+} -ik \bu^{\mu,+} = 0 \quad \bx \in \Gamma_{0} \, .
\end{equation}
From uniqueness of solutions to the exterior impedance problem, we
conclude that $\bu^{\mu,+}\equiv 0$ for $\bx$ in the exterior of 
$\Gamma_{0}$.
Thus $\bmu(\bx) = 0$ for $\bx \in \Gamma_{0}$.
Let $D_{j}$ denote the interior region of the obstacle boundary
$\Gamma_{j}$, for $j=1,2,\ldots n$. 
Recall that $\bu^{\mu}$ satisfies the Stokes-Helmholtz equation in $D_{j}$.
Using Green's identities for the Stokes-Helmholtz equations, we get 
\begin{equation}
\int_{D_{j}} |e(\bu^{\mu,+})|^{2}  - \overline{k}^{2} |\bu^{\mu,+}|^2) dV = 
\int_{\Gamma_{j}} \bu^{\mu,+} \cdot \overline{\ff}^{\mu,+} dS \, .
\end{equation}
Taking the imaginary part of the above equation and using~\cref{eq:bcaux}, 
we get
\begin{equation}
2 \text{Re}(k) \text{Im}(k) \int_{D_{j}} |\bu^{\mu,+}|^2 dV 
+ \text{Re}(k) \int_{\Gamma_{j}} |\bmu|^2 ds = 0 \, .
\end{equation}
This implies that $\bmu =0$ for all $\bx \in \Gamma_{j}$, $j=1,2,\ldots n$.

Finally, because $\bmu =0$ for all $\bx \in \Gamma$ and 
$c_{j}= 0$, $j=1,2,\ldots n$, 
we get that $w \equiv c_{0}$ for all $\bx \in \Omega$. 
Since $w\equiv 0$, it then follows that $c_{0} = 0$ as well, proving the 
injectivity of the system.

\end{proof}
\subsection{Existence results}
